\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2010-07-07 article.tex
Beginning of introduction, and added utf-8 support

% Introduction
%   Definitions
%     Patterns
%     Fundamental movements
%     Groups of techniques
%       blocks
%       strikes
%       thrusts
%       punches
%     Tagging
%  Problem statement

@@

% Use the following packages
\usepackage{dcolumn}            % Align table columns on decimal point
\usepackage{graphicx}           % Include graphics
\usepackage{listings}           % Pretty source code listings
\usepackage{url}                % Handle URLs better

@@

% Author information
\author{Bjorn Michelsen, III. Dan \\
  \texttt{<bjorn@bmichelsen.no>} \\
  \\
  ITF Tromsdalen School of Taekwon-Do \\
  Tromso, Norway
  }

@@

The Left Arm Bias in Taekwon-Do Patterns Chon-Ji to Juche

@@

Patterns in International Taekwon-Do Federation (ITF) are defined as a
choreographed sequence of fundamental movements, which represents an attack
or defense towards a particular target area or definite action of an
attacker, against one or several imaginary opponents.

These patterns are said to be using every available attacking and blocking
tool from different directions\cite{cyclo:vol1}. It has, however, recently
been observered that a right leg bias exist\cite{rlb}.

A study of arm techniques in patterns Chon-Ji to Juche, initiated in the hope
of uncovering whether or not there is a bias to either arm, is reported here.

A \emph{pattern} is a series of predefined basic elements called fundamental
movements. The \emph{fundamental movements} are attack or defensive techniques
against a specific target area or a predetermined action of an attacker.

Combined in a pattern, the student systematically deals with several imaginary
opponents under various assumptions, using every available attacking and
blocking tool from different directions\cite{cyclo:vol1}.

% Problem Statement
%
% pp. 154-155
% given the weight/importance of fundamental movements and patterns in the encyclopedia
% with approximately 3,200 techniques and
%Patterns, therefore,
%are the technical identity of Taekwon-Do.
% The following points should be considered while performing patterns:
%
%   9. Attack and defense techniques should be equally
%      distributed among right and left hands and feet
%
% and
%
% 'using every available attacking and blocking tool from different
% directions..'
%
% and the recent discovery of the right leg bias,
%
% Is there a bias towards the right or the left arm in ITF Taekwon-Do
% patterns Chon-Ji to Juche?
%
% note that Gibb's article includes *all* the patterns

Overall, there are a total of 152 kicks. 85 kicks are with the right
leg, and 67 kicks are with the left leg. This means that 56\% of all
kicks in patterns are with the right leg, whereas 44\% are with the left
leg.

@@

  Todo.

@@

    \bibitem{cyclo:vol1}
      Gen. Choi Hong Hi,
      \emph{Encyclopedia of Taekwon-Do}, Vol. 1, p. 154,
      International Taekwon-Do Federation, 1993.

@@

%\bibitem{key:foo}
%I. M. Author,
%``Some Related Article I Wrote,''
%{\em Some Fine Journal}, Vol. 17, pp. 1-100, 1987.

%\bibitem{foo:baz}
%A. N. Expert,
%{\em A Book He Wrote,}
%His Publisher, 1989.

>>>>

% Introduction
%   Definitions
%     Patterns
%     Fundamental movements
%  Related work
%  Problem statement
%     Groups of techniques
%       blocks
%       strikes
%       thrusts
%       punches
%     Tagging

@@

% Use the following packages
\usepackage[utf8]{inputenc}     % Support for UTF-8
\usepackage{dcolumn}            % Align table columns on decimal point
\usepackage{graphicx}           % Include graphics
\usepackage{listings}           % Pretty source code listings
\usepackage{url}                % Handle URLs better

@@

% Author information
\author{Bjørn Michelsen, III. Dan \\
  \texttt{<bjorn@bmichelsen.no>} \\
  \\
  ITF Tromsdalen School of Taekwon-Do \\
  Tromsø, Norway
  }

@@

@@

  A \emph{pattern} in International Taekwon-Do Federation (ITF) is defined as
  a choreographed sequence of fundamental movements. These \emph{fundamental
  movements} are basic elements which represent an attack or defense towards a
  specific target area, or a predetermined action of an attacker.

  Combined in a pattern, it allows the student to systematically deal with one
  or several imaginary opponents under various assumptions, using every
  available attacking and blocking tool from different directions. In
  addition, the techniques should also be evenly distributed between the left
  and the right side\cite{cyclo:vol1}.

  It has, however, recently been observed that a bias towards the right leg
  exist\cite{rlb}. % ALL patterns..

% how is related work written about?

% recent studies of a right leg bias; Recent work has found that..
%
% in this paper, therefore, we analyze..

%It has, however, recently been observed that a right leg bias
%exist\cite{rlb} when looking at all the 24 Taekwon-Do patterns.

% Is there a bias towards the *right* leg in Chon-Ji to Juche?

%A study of arm techniques in patterns Chon-Ji to Juche, initiated in the hope
%of uncovering whether or not there is a bias to either arm, is reported here.

% Problem Statement
%
% pp. 154-155
%
% The following points should be considered while performing patterns:
%
%   9. Attack and defense techniques should be equally
%      distributed among right and left hands and feet
%
%
%
% and the recent discovery of the right leg bias,
%
% Is there a bias towards the right or the left arm in ITF Taekwon-Do
% patterns Chon-Ji to Juche?
%
% note that Gibb's article includes *all* the patterns

%Overall, there are a total of 152 kicks. 85 kicks are with the right
%leg, and 67 kicks are with the left leg. This means that 56\% of all
%kicks in patterns are with the right leg, whereas 44\% are with the left
%leg.

@@

  % Odd-Magne Hansen for helping me with the terminology, and general feedback
  Todo.

@@

    \bibitem{cyclo:vol1}
      Gen. Choi Hong Hi,
      \emph{Encyclopedia of Taekwon-Do}, Vol. 1,
      International Taekwon-Do Federation, 1993.

@@
